Reanalysis Step 4: Propensity Score Analysis with Twang

### 2025-08-31 reanalysis-4-propensity_scores.qmd
deps

    # Run twang ps model - following analysis.Rmd approach
    twang_model <- ps(
      formula = ps_formula,
      data = data.frame(imputed_datasets[[i]]),  # Convert to data.frame as in analysis.Rmd
      n.trees = n_trees,
      interaction.depth = 3,
      shrinkage = 0.01,
      estimand = "ATT",
      stop.method = c("es.mean"),  # Using es.mean only for speed
      verbose = FALSE
    )

@@

  # Export necessary objects to cluster
  clusterExport(cl, c(
    "cache_dir", "use_cache", "ps_formula", "imputed_datasets",
    "n_trees", "ps", "get.weights"
  ))

>>>>

    # Get the data for this imputation and ensure lapse is numeric
    imp_data <- data.frame(imputed_datasets[[i]])

    # Ensure lapse is numeric 0/1 (required by twang)
    if (!is.numeric(imp_data$lapse)) {
      imp_data$lapse <- as.numeric(as.character(imp_data$lapse))
    }

    # Run twang ps model - following analysis.Rmd approach
    twang_model <- ps(
      formula = ps_formula,
      data = imp_data,
      n.trees = n_trees,
      interaction.depth = 3,
      shrinkage = 0.01,
      estimand = "ATT",
      stop.method = c("es.mean"),  # Using es.mean only for speed
      verbose = FALSE
    )

@@

  # Export necessary objects to cluster
  clusterExport(cl, c(
    "cache_dir", "use_cache", "ps_formula", "imputed_datasets",
    "n_trees", "process_imputation"
  ), envir = environment())
